NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-09-01 paper/Chapters/Chapter2.tex
pdf prepared to be submitted

Participants were required to keep a diary that record everything eaten or drunk over four consecutive days. Interviewers undertook three visits with each participant. At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day. The second visit was a brief one to check for compliance, answer potential questions, and deal with problems. Interviewers also reviewed the diary to identify and edit possible omissions and missing detail in the food diary. The third visit was to collect the diary and again review and edit possible omissions.

>>>>

Participants were required to keep a diary that record everything eaten or drunk over four consecutive days. Interviewers undertook three visits with each participant. At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day. The second visit was a brief one to check for compliance, and answer potential questions from the participants. Interviewers also reviewed the diary to identify and edited possible omissions and missing detail in the food diary. The third visit was to collect the diary and again review and edit possible omissions.
